Exploration

### 2018-03-11 exploration.Rmd
beginning code for samples from S

## Observed datasets
The simulated species *S* is sampled appropriately in order to fit each SDM model. The observed datasets,*O*, may be random or intentionally biased to mimic common issues with empirical data.
### Correlative: MaxEnt
```{r O_Mx}
library(dismo)
Mx.n <- 3000
Mx.P <- sample((1:nrow(lam.df))[lam.df$lambda > 1], Mx.n, replace=T)
pres <- 1:nrow(lam.df) %in% Mx.P
Mx.out <- maxent(x=lam.df[,c(1,3,5:9)], p=pres)
lam.df$MxPred <- 1:nrow(lam.df) %in% row.names(Mx.out@presence)
lam.df$MxCorrect <- with(lam.df, (MxPred==1 & lambda > 1) |
                           (MxPred==0 & lambda < 1))
ggplot(lam.df, aes(x=lon, y=lat, fill=MxCorrect)) + geom_tile()
```
### Mechanistic: CA
```{r O_CA}

>>>>

## Observed datasets
The simulated species *S* is sampled appropriately in order to fit each SDM model. The observed datasets,*O*, may be random or intentionally biased to mimic common issues with empirical data. The realized simulated data generated above (`d` and its abundance summary `N_sim`) are the underlying true distribution. The samples will be drawn from occupied cells in the final time steps where the species is approximately at equilibrium.
```{r O_setup}
O_n <- c(Mx=500, CA=20, IPM=20) # number of cells in sample
```

### Correlative: MaxEnt
```{r O_Mx}
library(dismo)
Mx.P <- sample((1:nrow(lam.df))[lam.df$lambda > 1], O_n$Mx, replace=T)
pres <- 1:nrow(lam.df) %in% Mx.P
Mx.out <- maxent(x=lam.df[,c(1,3,5:9)], p=pres)
lam.df$MxPred <- 1:nrow(lam.df) %in% row.names(Mx.out@presence)
lam.df$MxCorrect <- with(lam.df, (MxPred==1 & lambda > 1) |
                           (MxPred==0 & lambda < 1))
ggplot(lam.df, aes(x=lon, y=lat, fill=MxCorrect)) + geom_tile()
```
### Mechanistic: CA
```{r O_CA}
